### 2012-02-27 supplementary.tex
Early work on the supplemental material

>>>>

\begin{figure}[h]
\centering
  \includegraphics[width=13cm]{oscillations_gas_dependence_supplemental.png}
  \caption{Complete series of oscillating sample. For every frame the CO-concentration is increased.}
  \label{fgr:gas_dependence}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=9cm]{oscillations_gas_dependence_summary_supplemental.png}
  \caption{Summary of the gas-dependence. The overall trend of increasing oscillation period is now supporimposed by small discontinous stpes when the CO concentration is increased.}
  \label{fgr:gas_dependence_summary}
\end{figure}

\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{temperature_dependence_supplemental.png}
  \caption{Another example of the very pronounced temperature dependence. In this case the oscillations are switched on and off by a step of 20$^\circ$C}
  \label{fgr:temperature_dependence_supplemental}
\end{figure}

\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{duty_cycles_long_measurement_supplemental.png}
  \caption{A plot of the duty-cycle of the sample duing the 4-day long experiment}
  \label{fgr:temperature_dependence_supplemental}
\end{figure}

\footnotesize{
\bibliography{literature} %your .bib file
\bibliographystyle{rsc} %the RSC's .bst file
}
